P.berghei pir analysis

### 2021-09-07 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
save biplot in plots dir
improve biplot

#Calculate the highest loadings, only want these labels

pca_object_loadings$Geneid <- ''

highest_loadings <- pca_object_loadings[rev(
    order(
      apply(
        abs(
          data.frame(pca_object_loadings$PC1, 
                     pca_object_loadings$PC2)),
        1,
        sum)
    )
  )[1:10],]

pca_object_loadings[rev(
  order(
    apply(
      abs(
        data.frame(pca_object_loadings$PC1, 
                   pca_object_loadings$PC2)),
      1,
      sum)
  )
)[1:10],]$Geneid <- 
  allgene.info$Description[match(rownames(highest_loadings),
  allgene.info$Geneid)]

plot +
  geom_point(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005),
             inherit.aes = FALSE, size = 0.75) +
  geom_label_repel(data = pca_object_loadings,
             aes(x = PC1*0.005, y = PC2*0.005,
                 label = Geneid),
             inherit.aes = FALSE, size = 3,
            nudge_x = 0.4,
            force = 100)
```

>>>>

#Calculate the highest loadings, only want these labels
top_loadings <- 15
pca_object_loadings$Geneid <- ''

highest_loadings <- pca_object_loadings[rev(
    order(
      apply(
        abs(
          data.frame(pca_object_loadings$PC1, 
                     pca_object_loadings$PC2)),
        1,
        sum)
    )
)[1:top_loadings],]

highest_loadings$Geneid <- 
  gsub(
    gsub(allgene.info$Description[match(rownames(highest_loadings),
                                      allgene.info$Geneid)], 
       pattern = 'putative',
       replacement = 'put.'),
    pattern = 'early transcribed membrane protein',
    replacement = 'ETRAMP')

loadings_scale <- 0.005

(bp <- plot +
  geom_point(data = highest_loadings,
             aes(x = PC1*loadings_scale, y = PC2*loadings_scale),
             inherit.aes = FALSE, size = 0.75) +
  geom_text_repel(data = highest_loadings,
             aes(x = PC1*loadings_scale, y = PC2*loadings_scale,
                 label = Geneid),
             inherit.aes = FALSE, 
             size = 3,
             min.segment.length = 0,
            force = 100
            ) )

ggsave('plots/thesis_chapter3_figure_biplot.png',
       width = 7,
       height = 5,
       units = "in",
       bp)
